---
title: "Untitled"
output: html_document
date: "2024-11-26"
---

## 读取数据

load package

```{r}
#library a bunch of packages we may (or may not) use - install them first if not installed already. 
library(tidyverse)
library(tmap)
library(plotly)
library(broom)
library(mapview)
library(sf)
library(sp)
library(spdep)
library(car)
library(fs)
library(janitor)
```

read data

```{r}
#读取病房数据
#download a zip file containing some boundaries we want to use

download.file("https://data.london.gov.uk/download/statistical-gis-boundary-files-london/9ba8c833-6370-4b11-abdc-314aa020d5e0/statistical-gis-boundaries-london.zip",
              destfile="data/statistical-gis-boundaries-london.zip")
# 解压
listfiles<-dir_info(here::here("data")) %>%
  dplyr::filter(str_detect(path, ".zip")) %>%
  dplyr::select(path)%>%
  pull()%>%
  #print out the .gz file
  print()%>%
  as.character()%>%
  utils::unzip(exdir=here::here("data"))

# 读取边界数据
#look what is inside the zip

Londonwards<-fs::dir_info(here::here("data", 
                                 "statistical-gis-boundaries-london", 
                                 "ESRI"))%>%
  #$ means exact match
  dplyr::filter(str_detect(path, 
                           "London_Ward_CityMerged.shp$"))%>%
  dplyr::select(path)%>%
  dplyr::pull()%>%
  #read in the file in
  sf::st_read()

#check the data
qtm(Londonwards)
```

其他数据

```{r}
#read in some attribute data
LondonWardProfiles <- read_csv("https://data.london.gov.uk/download/ward-profiles-and-atlas/772d2d64-e8c6-46cb-86f9-e52b4c7851bc/ward-profiles-excel-version.csv",
                               col_names = TRUE,
                               locale = locale(encoding = 'Latin1'))

# 读入并清理属性数据
LondonWardProfiles <- read_csv("https://data.london.gov.uk/download/ward-profiles-and-atlas/772d2d64-e8c6-46cb-86f9-e52b4c7851bc/ward-profiles-excel-version.csv", 
                               na = c("", "NA", "n/a"), 
                               locale = locale(encoding = 'Latin1'), 
                               col_names = TRUE)

#check all of the columns have been read in correctly
Datatypelist <- LondonWardProfiles %>% 
  summarise_all(class) %>%
  pivot_longer(everything(), 
               names_to="All_variables", 
               values_to="Variable_class")

Datatypelist
```

使用通用 ID 将两者合并在一起，使用病房代码

```{r}
#merge boundaries and data
LonWardProfiles <- Londonwards%>%
  left_join(.,
            LondonWardProfiles, 
            by = c("GSS_CODE" = "New code"))

#let's map our dependent variable to see if the join has worked:
tmap_mode("plot")
qtm(LonWardProfiles, 
    fill = "Average GCSE capped point scores - 2014", 
    borders = NULL,  
    fill.palette = "Blues")
```

添加学校数据

```{r}
#might be a good idea to see where the secondary schools are in London too
london_schools <- read_csv("https://data.london.gov.uk/download/london-schools-atlas/57046151-39a0-45d9-8dc0-27ea7fd02de8/all_schools_xy_2016.csv")

#from the coordinate values stored in the x and y columns, which look like they are latitude and longitude values, create a new points dataset
lon_schools_sf <- st_as_sf(london_schools, 
                           coords = c("x","y"), 
                           crs = 4326)

lond_sec_schools_sf <- lon_schools_sf %>%
  filter(PHASE=="Secondary")

tmap_mode("plot")
qtm(lond_sec_schools_sf)
```

## 分析GCSE考试成绩

使用不同的回归模型，探索影响GCSE考试成绩的因素\
**1.研究问题：哪些因素可能导致整个城市的平均 GCSE 分数存在差异？**

回归基础：线性关系---散点图
```{r}
q <- qplot(x = `Unauthorised Absence in All Schools (%) - 2013`, 
           y = `Average GCSE capped point scores - 2014`, 
           data=LonWardProfiles)
#plot with a regression line - note, I've added some jitter here as the x-scale is rounded
q + stat_smooth(method="lm", se=FALSE, size=1) + 
  geom_jitter()

```
在R中运行回归模型
```{r}
# 1.清理并筛选数据
#run the linear regression model and store its outputs in an object called model1
Regressiondata<- LonWardProfiles%>%
  clean_names()%>%
  dplyr::select(average_gcse_capped_point_scores_2014, 
                unauthorised_absence_in_all_schools_percent_2013)

#now model
model1 <- Regressiondata %>%
  lm(average_gcse_capped_point_scores_2014 ~
               unauthorised_absence_in_all_schools_percent_2013,
     data=.)

#show the summary of those outputs
summary(model1)
```
解释
1. Coefficient Estimates：β0（截距）和 β1（斜率）参数估计值来自方程1。您会注意到，β0=371.471和β1= −41.237
2. Coefficient Standard Errors：如果未经授权缺勤增加 1%，虽然模型显示我们可能预计 GSCE 分数会下降 -41.2分，但平均而言可能会下降约 1.9 分。tips：系数代表 1 个单位的变化，这里是 %，因为变量是未经授权缺课的百分比，所以 1 个单位代表 1% 的变化
3. R方：本例中，r2值为 0.42 表明 GCSE 成绩的大约 42% 的变化可以用未经批准缺勤的变化来解释

broom整理输出
```{r}
library(broom)
tidy(model1)
glance(model1)

# 每个点的预测
library(tidypredict)
Regressiondata %>%
  tidypredict_to_column(model1)
```
tidymodels包进行线性回归分析
```{r}
library(tidymodels)

# set the model
lm_mod <- linear_reg()

# fit the model
lm_fit <- 
  lm_mod %>% 
  fit(average_gcse_capped_point_scores_2014 ~
               unauthorised_absence_in_all_schools_percent_2013,
     data=Regressiondata)

# we cover tidy and glance in a minute...
tidy(lm_fit)

glance(lm_fit)
```


 
