---
title: "Untitled"
output: html_document
date: "2024-11-12"
---

## Q:对于任何一个伦敦行政区，该行政区内的蓝色牌匾是随机分布的还是呈现出某种分散或聚集的模式？

## 读数据，spatstat包中的点模式分析功能

```{r}
#first library a few packages that we will use during the practical
library(spatstat)
library(here)
library(sp)
library(tmap)
library(sf)
library(tmaptools)

```

### 1.get the London Borough Boundaries

```{r}
LondonBoroughs <- st_read(here::here("data", "statistical-gis-boundaries-london", "ESRI", "London_Borough_Excluding_MHW.shp"))
st_crs(LondonBoroughs)

```

### 2.查找与伦敦（E09）相关的地区代码位

```{r}
library(stringr)
BoroughMap <- LondonBoroughs %>%
  dplyr::filter(str_detect(GSS_CODE, "^E09"))%>%
  st_transform(., 27700)

qtm(BoroughMap)
summary(BoroughMap)
# st_crs(BoroughMap)

```

### 3.读取英国所有蓝色牌匾的位置

```{r}
##Now get the location of all Blue Plaques in the City
BluePlaques <- st_read("https://s3.eu-west-2.amazonaws.com/openplaques/open-plaques-london-2018-04-08.geojson")
summary(BluePlaques)

#plot the blue plaques in the city
tmap_mode("plot")
tm_shape(BoroughMap) +
  tm_polygons(col = NA, alpha = 0.5) +
tm_shape(BluePlaques) +
  tm_dots(col = "blue")
```

## 数据清理，移除行政区外的点

```{r}
#remove duplicates
library(tidyverse)

library(sf)
BluePlaques <- distinct(BluePlaques)
st_crs(BluePlaques)

# 将x转换为y的CRS
BluePlaques <- st_transform(BluePlaques, crs = st_crs(BoroughMap))  

```

## 空间子集

```{r}
# 保留 BluePlaques 中所有与 BoroughMap 的几何边界有空间关系的点
# 默认的拓扑关系是 intersects（相交）
BluePlaquesSub <- BluePlaques[BoroughMap,]

#check to see that they've been removed
tmap_mode("plot")
tm_shape(BoroughMap) +
  tm_polygons(col = NA, alpha = 0.5) +
tm_shape(BluePlaquesSub) +
  tm_dots(col = "blue")

# add sparse=false to get the complete matrix.
intersect_indices <-st_intersects(BoroughMap, BluePlaques)

```

## 空间连接

将左侧数据集（在左连接中）更改为 OSM 数据

```{r}
Londonborough <- st_read(here::here("data",
                                    "statistical-gis-boundaries-london", 
                                    "ESRI", 
                                    "London_Borough_Excluding_MHW.shp"))%>%
  st_transform(., 27700)

OSM <- st_read(here::here("data",
                          "greater-london-latest-free.shp", 
                          "gis_osm_pois_a_free_1.shp")) %>%
  st_transform(., 27700) %>%
  #select hotels only
  filter(fclass == 'hotel')

# 将 OSM 中的酒店数据与 Londonborough 中的行政区数据进行连接
join_example <-  st_join(OSM, Londonborough)

nrow(join_example)

```
上周的airbnb数据
```{r}
# read in the .csv
# and make it into spatial data

Airbnb <- read_csv("D:/1UCL/casa0005/gis/prac5/data/listings.csv") %>%
  st_as_sf(., coords = c("longitude", "latitude"), 
                   crs = 4326) %>%
    st_transform(., 27700)%>%
    #select entire places that are available all year
    filter(room_type == 'Entire home/apt' & availability_365 =='365')


# make a function for the join
# functions are covered in practical 7
# but see if you can work out what is going on
# hint all you have to do is replace data1 and data2
# with the data you want to use

Joinfun <- function(data1, data2){

output<- data1%>%
  st_join(Londonborough,.) %>%
  add_count(GSS_CODE, name="hotels_in_borough") 

  return(output)
}

# use the function for hotels
Hotels <- Joinfun(OSM, Londonborough)

# then for airbnb
Airbnb <- Joinfun(Airbnb, Londonborough)
 
Hotels <- Hotels %>%
  #at the moment each hotel is a row for the borough
  #we just one one row that has number of airbnbs
  group_by(., GSS_CODE, NAME)%>%
  summarise(`Accomodation count` = unique(hotels_in_borough))

Airbnb <- Airbnb %>%
  group_by(., GSS_CODE, NAME)%>%
  summarise(`Accomodation count` = unique(hotels_in_borough))

```
连接对象
st_join默认使用st_intersects()。这意味着对于酒店数据，
airbnb与每个酒店行政区相交的地方都会添加一个新行。
```{r}
# left_join<- left_join(Hotels, Airbnb,
#             by = c("GSS_CODE" = "GSS_CODE"))
all_accomodation <- st_join(Hotels, Airbnb)

head(all_accomodation)
```
将参数更改为st_equals()
```{r}
all_accomodation2 <- st_join(Hotels, Airbnb, join = st_equals)

head(all_accomodation2)
```
## 选择研究区域为Harrow
```{r}
#extract the borough

# select by attribute
Harrow <- BoroughMap %>%
  filter(., NAME=="Harrow")

#Check to see that the correct borough has been pulled out
tm_shape(Harrow) +
  tm_polygons(col = NA, alpha = 0.5)

#clip the data to our single borough
BluePlaquesSub <- BluePlaques[Harrow,]
#check that it's worked
tmap_mode("plot")

tm_shape(Harrow) +
  tm_polygons(col = NA, alpha = 0.5) +
tm_shape(BluePlaquesSub) +
  tm_dots(col = "blue")
```

### 开始分析spatstat
1.创建一个观察窗口
2.创建一个点模式ppp对象
```{r}
#now set a window as the borough boundary
window <- as.owin(Harrow)
plot(window)

#create a sp object
BluePlaquesSub<- BluePlaquesSub %>%
  as(., 'Spatial')
#create a ppp object
BluePlaquesSub.ppp <- ppp(x=BluePlaquesSub@coords[,1],
                          y=BluePlaquesSub@coords[,2],
                          window=window)
BluePlaquesSub@coords[,1]

BluePlaquesSub.ppp %>%
  plot(.,pch=16,cex=0.5, 
       main="Blue Plaques Harrow")
```

## 点密度分析
### 1.核密度分析
```{r}
BluePlaquesSub.ppp %>%
  density(., sigma=500) %>%
  plot()

BluePlaquesSub.ppp %>%
  density(., sigma=1000) %>%
  plot()

```
### 2.样方分析
```{r}
#First plot the points
plot(BluePlaquesSub.ppp,
     pch=16,
     cex=0.5, 
     main="Blue Plaques in Harrow")

#now count the points in that fall in a 6 x 6
#grid overlaid across the windowBluePlaquesSub.ppp2<-BluePlaquesSub.ppp %>%
BluePlaquesSub.ppp %>%
  quadratcount(.,nx = 6, ny = 6)%>%
    plot(., add=T, col="red")
```

```{r}
#run the quadrat count
Qcount <- BluePlaquesSub.ppp %>%
  quadratcount(.,nx = 6, ny = 6) %>%
  as.data.frame() %>%
  dplyr::count(Var1=Freq)%>%
  dplyr::rename(Freqquadratcount=n)

Qcount %>% 
  summarise_all(class)


```
```{r}
sums <- Qcount %>%
  #calculate the total blue plaques (Var * Freq)
  mutate(total = Var1 * Freqquadratcount) %>%
  dplyr::summarise(across(everything(), sum))%>%
  dplyr::select(-Var1) 

lambda<- Qcount%>%
  #calculate lambda
  mutate(total = Var1 * Freqquadratcount)%>%
  dplyr::summarise(across(everything(), sum)) %>%
  mutate(lambda=total/Freqquadratcount) %>%
  dplyr::select(lambda)%>%
  pull(lambda)

QCountTable <- Qcount %>%
  mutate(Pr=((lambda^Var1)*exp(-lambda))/factorial(Var1))%>%
  #now calculate the expected counts based on our total number of plaques
  #and save them to the table
  mutate(Expected= (round(Pr * sums$Freqquadratcount, 0)))

#Compare the frequency distributions of the observed and expected point patterns
plot(c(1,5),c(0,14), type="n",
xlab="Number of Blue Plaques (Red=Observed,Blue=Expected)", 
     ylab="Frequency of Occurances")
points(QCountTable$Freqquadratcount, 
       col="Red", 
       type="o", 
       lwd=3)
points(QCountTable$Expected, col="Blue", 
       type="o", 
       lwd=3)

teststats <- quadrat.test(BluePlaquesSub.ppp, nx = 6, ny = 6)
plot(BluePlaquesSub.ppp,pch=16,cex=0.5, main="Blue Plaques in Harrow")
plot(teststats, add=T, col = "red")
```
### 3.Ripley’s K
```{r}
K <- BluePlaquesSub.ppp %>%
  Kest(., correction="border") %>%
  plot()

Kval <- as.data.frame(Kest(BluePlaquesSub.ppp, correction = "Ripley"))
```
### 4.DBSCAN
```{r}
# install.packages("fpc")
library(fpc)
#first check the coordinate reference system of the Harrow spatial polygon:
st_geometry(BoroughMap)

#first extract the points from the spatial points data frame
BluePlaquesSubPoints <- BluePlaquesSub %>%
  coordinates(.)%>%
  as.data.frame()

#now run the dbscan analysis
db <- BluePlaquesSubPoints %>%
  fpc::dbscan(.,eps = 700, MinPts = 4)

#now plot the results
plot(db, BluePlaquesSubPoints, main = "DBSCAN Output", frame = F)
plot(BoroughMap$geometry, add=T)

# used to find suitable eps value based on the knee in plot
# k is no of nearest neighbours used, use min points
# install.packages("dbscan")
library(dbscan)

BluePlaquesSubPoints%>%
  dbscan::kNNdistplot(.,k=4)
```

地图
```{r}
library(ggplot2)
db
db$cluster
BluePlaquesSubPoints<- BluePlaquesSubPoints %>%
  mutate(dbcluster=db$cluster)


chulls <- BluePlaquesSubPoints %>%
  group_by(dbcluster) %>%
  dplyr::mutate(hull = 1:n(),
  hull = factor(hull, chull(coords.x1, coords.x2)))%>%
  arrange(hull)

#chulls2 <- ddply(BluePlaquesSubPoints, .(dbcluster), 
              #  function(df) df[chull(df$coords.x1, df$coords.x2), ])

chulls <- chulls %>%
  filter(dbcluster >=1)

dbplot <- ggplot(data=BluePlaquesSubPoints, 
                 aes(coords.x1,coords.x2, colour=dbcluster, fill=dbcluster)) 
#add the points in
dbplot <- dbplot + geom_point()
#now the convex hulls
dbplot <- dbplot + geom_polygon(data = chulls, 
                                aes(coords.x1,coords.x2, group=dbcluster), 
                                alpha = 0.5) 
#now plot, setting the coordinates to scale correctly and as a black and white plot 
#(just for the hell of it)...
dbplot + theme_bw() + coord_equal()

###add a basemap
##First get the bbox in lat long for Harrow
HarrowWGSbb <- Harrow %>%
  st_transform(., 4326)%>%
  st_bbox()

library(OpenStreetMap)

basemap <- OpenStreetMap::openmap(c(51.5549876,-0.4040502),c(51.6405356,-0.2671315),
                         zoom=NULL,
                         "osm")

  # convert the basemap to British National Grid
basemap_bng <- openproj(basemap, projection="+proj=tmerc +lat_0=49 +lon_0=-2 +k=0.9996012717 +x_0=400000 +y_0=-100000 +ellps=airy +nadgrids=OSTN15_NTv2_OSGBtoETRS.gsb +units=m +no_defs +type=crs")

#autoplot(basemap_bng) sometimes works
autoplot.OpenStreetMap(basemap_bng)+ 
  geom_point(data=BluePlaquesSubPoints, 
             aes(coords.x1,coords.x2, 
                 colour=dbcluster, 
                 fill=dbcluster)) + 
  geom_polygon(data = chulls, 
               aes(coords.x1,coords.x2, 
                   group=dbcluster,
                   fill=dbcluster), 
               alpha = 0.5)  
```

